Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-10 draft.tex
merge

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
and $y \otimes \beta$ is defined by
\begin{align*}
\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
\brian{how to say this now}
\end{proof}

@@

We turn towards a model for the $\EE_n$ center as a constructible factorization algebra.

Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Define the complex
\[
\begin{tikzcd}
& \ul{0} & \ul{1} \\
\Tilde{\Omega}^\bu (\RR_{\geq 0}) = & \Omega^0 (\RR_{\geq 0}) \ar[r, "j^* \circ \d_{\rm dR}"] & \Omega^1(\RR_{>0})  .
\end{tikzcd}
\]
The commutative dg algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the rule
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

@@

\begin{proof}
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U) \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [2]$. 
Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
and $y \otimes \beta$ is defined by
\begin{align*}
\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
\end{align*}
Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. \brian{how to say this now}
The bracket is extended to the entire symmetric algebra by using the graded Leibniz rule.
\end{proof}

@@

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \otimes \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
The map $\int_{\RR_{>0}}$ induces a map of factorization algebras on $M$
\[
\int_{\RR_{>0}} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$. 
Using the retract $r_\phi$, we see that this is a quasi-isomorphism of factorization algebras on $M$.

Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras $\int_{\RR_{\geq 0}} : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg)$.
\brian{I should spell this out now.}

The pair $(\int_{\RR_{>0}} , \int_{\RR_{\geq 0}})$ is a quasi-isomorphisms of factorization sc-pairs. 
The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
\end{proof}

@@

\owen{Brian: please edit this paragraph.}
Although we have started here with a Lie group $G$, 
one can replace $T^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
Of particular interest to us here are the shifted cotangent spaces~$T^*[n] X$.

>>>>

Next, recall that to an open set $U \subset M$ the factorization algebra ${\rm Gr} \; \bZ_n (\fg)$ assigns the cochain complex
\[
\clie^\bu\bigg(\fg \otimes \Omega^\bu (U) \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c(U) [1]\right) \bigg) = {\rm Hom}^\bu \bigg(\cliels(\fg \otimes \Omega^\bu(U)) , \cliels (\fg \otimes \Omega^\bu_c(U)) \bigg).
\]
We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[1] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[1]$. 
Define $\{F, G\} \in k$ by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c(U)[1] \hookrightarrow \fg \otimes \Omega^\bu(U)[1] \xto{F} k
\]
where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
We extend this to a bracket on the full complex by the graded Leibniz rule.

%Let $x^* \otimes \alpha$ denote an homorphism of the form $\fg \otimes \Omega (U)[1] \to \Sym^0 = k$ and $y \otimes \beta$ denote a homomorphism $k = \Sym^0 \to \fg \otimes \Omega_c(U) [1]$. 
%Then, the bracket involving the linear elements $x^* \otimes \alpha$ 
%and $y \otimes \beta$ is defined by
%\begin{align*}
%\{x^* \otimes \alpha  , y \otimes \beta \} & = \<x^*, y\>_\fg \int_U \alpha \beta \\
%\{x^* \otimes \alpha , x'^* \otimes \alpha' \} & = 0 \\
%\{y \otimes \beta , y' \otimes \beta'\} & = 0 . 
%\end{align*}
%Here, $\<x^*, y\>_\fg$ denotes the linear pairing between $\fg$ and $\fg^*$ and $\int_U\alpha \beta$ denotes the linear pairing between compactly supported distributional differential forms and differential forms. 
%\brian{how to say this now}
\end{proof}

@@

We turn towards a model for the $\EE_n$-center as a constructible factorization algebra on an $(n+1)$-manifold with boundary.

Before stating the definition of this model, we introduce the following variant of the de Rham complex of differential forms on $\RR_{\geq 0}$. 
Let $j : \RR_{>0} \hookrightarrow \RR_{\geq 0}$ be the embedding of the open ray into the closed ray. 
Let $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ be the two-term complex
\[
\Omega^0(\RR_{\geq 0}) \xto{j^* \circ \d_{\rm dR}} \Omega^1(\RR_{>0})[-1]  .
\]
The commutative dg algebra structure on $\Tilde{\Omega}^\bu (\RR_{\geq 0})$ is defined by the rule
\[
f \cdot (g \, \d t) = (j^* f) g\, \d t .
\]

@@

\begin{proof}
For $U \subset M \times \RR_{>0}$ the underlying graded vector space of $\bC_n(\fg)(U)$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (U)[1]) \; , \; {\rm Sym}  \left(\fg \otimes \Omega^\bu_c(U) [2] \right) \right)  .
\]
The Poisson structure is described in a similar way as in the proof of Lemma \ref{lmm:pois1}. 
We first define the bracket $\{F,G\}$ between the following simple elements $F : \fg \otimes \Omega^\bu (U)[2] \to k$ and $G : k \to \fg \otimes \Omega^\bu_c(U)[2]$. 
Define $\{F, G\} \in k$ by the composition
\[
k \xto{G} \fg \otimes \Omega^\bu_c(U)[2] \hookrightarrow \fg \otimes \Omega^\bu(U)[2] \xto{F} k
\]
where the middle arrow uses the obvious inclusion of compactly supported de Rham forms inside of all de Rham forms. 
Notice that this bracket has cohomological degree $+1$ as desired.
We extend this to a bracket on the full complex by the graded Leibniz rule.

Next, we define the $\PP_0$-bracket for the value of the factorization algebra on open sets of the form $V \times [0,\epsilon)$. 
Notice that the underlying graded vector space of $\bC_n(\fg)(V \times [0,\epsilon))$ is of the form
\[
{\rm Hom}^\bu\left(\Sym(\fg \otimes \Omega^\bu (V) \otimes \Tilde{\Omega}^\bu ([0,\epsilon))) [1]) \; , \; \Sym \left(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2] \right) \right)  .
\]
We first define the bracket $\{F,G\}$ between the following simple elements 
\[
F : \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \to k
\]
and 
\[
G : k \to \fg \otimes \Omega^\bu_c(V \times [0,\epsilon))[2] .
\]
Define $\{F, G\}$ by the composition
\[
\begin{tikzcd}
k \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[rdd, dotted, "{\{F,G\}}"'] \ar[r, "G \otimes 1"] & 
\bigg(\fg \otimes \Omega^\bu_c(V \times [0,\epsilon)) [2]\bigg) \otimes \bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) \bigg) \ar[d,"{[\cdot, \cdot]}"] \\
& \fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu([0,\epsilon)) [2] \ar[d, "F"] \\ & k
\end{tikzcd}
\]
The middle bracket is induced from the Lie bracket on $\fg$ and the wedge product of differential forms.
Again, this bracket is extended to the full algebra by the Leibniz rule.
\end{proof}

@@

Notice that for an open set $V \subset M$ we have 
\[
\bC_n(\fg)^{\circ} (V) = \clies \bigg(\fg \otimes \Omega (V \otimes \RR_{>0} ) \; , \; \Sym \left(\fg \otimes \Omega_c(V \times \RR_{>0}) [2] \right) \bigg)  .
\]
Integration along $\RR_{>0}$ induces a map of factorization algebras on $M$
\[
I^{\circ} : \bC_n(\fg)^\circ \to {\rm Gr} \; \bZ_n (\fg)
\]
which on linear elements in ${\rm Sym}(\fg \otimes \Omega^\bu_c (V \times \RR_{>0})$ sends $x \otimes \alpha \in \Omega^\bu_c(V \times \RR_{>0})[2]$ to $x \otimes \int_{\RR_{>0}} \alpha \in \Omega^\bu_c (V)[1]$.

Next, using the map $r_\phi$, define a map of factorization algebras
\[
r_\phi^\circ : {\rm Gr} \; \bZ_n (\fg) \to \bC_n(\fg)^\circ
\]
as follows. 
For an open set $V \subset M$, define $r_{\phi}^\circ (V)$ on linear elements $x \otimes \alpha$ in $\Sym(\fg \otimes \Omega^\bu(V)_c[1])$ by
\[
r_\phi^\circ (U) (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t)  .
\]
This map can be extended to all of ${\rm Gr} \; \bZ_n(\fg)$ in a similar fashion. 
One can show that $r_\phi^\circ$ is a deformation retract of $I^\partial$.
In particular, $I^\partial$ is a quasi-isomorphism of factorization algebras on $M$.

Similarly, integration of compactly supported forms along $\RR_{\geq 0}$ determines a quasi-isomorphism of factorization algebras 
\[
I^\partial : \bC_n(\fg)^\partial \to {\rm Gr} \; \bU_n(\fg) .
\]
Recall that for $V \subset M$ we have
\[
\bC_n(\fg)^\partial (V) = \clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) .
\]
On $V$, the map $I^\partial (V)$ is defined by the composition
\[
\begin{tikzcd}
\clies\bigg(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})  \; , \; \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \bigg) \ar[r, "{{\rm ev}_1}"] & \Sym\left(\fg \otimes \Omega^\bu_c (V \times \RR_{\geq 0})[2] \right) \ar[d, "{\int_{\RR_{\geq 0}}}"] \\ &  \Sym\left(\fg \otimes \Omega^\bu_c (V)[1] \right) .
\end{tikzcd}
\]
The first map ${\rm ev}_1$ evaluates the unit in $\Sym \left(\fg \otimes \Omega^\bu(V) \Hat{\otimes} \Tilde{\Omega}^\bu(\RR_{\geq 0})\right)$ and the second map is induced by integration along $\RR_{\geq 0}$. 
It is immediate to check that $I^{\partial}$ extends to a map of factorization algebras.

For an open set $V$ the cochain map $I^{\partial}(V)$ admits the following explicit retract $r_\phi^\partial(V)$ defined on linear elements $x \otimes \alpha$ in $\Sym (\fg \otimes \Omega^\bu_c(V)[1])$ by the formula
\[
r_{\phi}^\partial (x \otimes \alpha) = x \otimes (\pi^* \alpha \wedge \phi \d t) \pm \d_{\rm CE} (x \otimes \pi^* \alpha \phi ) .
\]
The map $r_\phi^\partial (V)$ is extended to the entire symmetric algebra in the obvious way.

We have shown that $(I^{\circ}, I^\partial)$ is a quasi-isomorphism of factorization sc-pairs. 
The compatibility of this quasi-isomorphism with Poisson brackets is a direct calculation. 
\end{proof}

@@

Although we have started here with a Lie group $G$, 
one can replace ${\rm T}^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
Of particular interest to us here are the shifted cotangent spaces~${\rm T}^*[n] X$.
